\TitleFont Calorinator - an interactive floor game to perform fitness exercises

### 2015-01-25 paper.tex
Added walkthrough

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{hyperref}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\newcommand*{\TitleFont}{%
      \usefont{\encodingdefault}{\rmdefault}{b}{n}%
      \fontsize{16}{20}%
      \selectfont}

@@

TBD

>>>>

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{hyperref}
\usepackage{helvet}
\usepackage{color}
\renewcommand{\familydefault}{\sfdefault}
\newcommand*{\TitleFont}{%
      \usefont{\encodingdefault}{\rmdefault}{b}{n}%
      \fontsize{16}{20}%
      \selectfont}

@@

In this scenario the student Andy trains his body by running in place, jumping a lot, staying in push-ups position and alternating running and touching the floor.

\textcolor{white}{
Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text Text
}

\begin{figure}[!htb]
\minipage{.15\textwidth}
  \includegraphics[width=\linewidth]{graphics/Image.jpg}
\endminipage\hfill
\minipage{.15\textwidth}
  \includegraphics[width=\linewidth]{graphics/Image(2).jpg}
\endminipage\hfill
\minipage{.15\textwidth}%
  \includegraphics[width=\linewidth]{graphics/Image(3).jpg}
\endminipage
  \caption{Task Overview. (1) Andy runs in place and jumps over trees. (2) Water appeared  with some ice floes on it and Andy has to stay on these, but they melt. (3) Andy has to build a bridge to cross the water.}\label{fig:awesome_image3}
\end{figure}

The conrete beginning of the game (Figure 3 (1)) includes more thoughts. We focus on it in detail.

\begin{figure}[!htb]
\minipage{.15\textwidth}
  \includegraphics[width=\linewidth]{graphics/Image(4).jpg}
\endminipage\hfill
\minipage{.15\textwidth}
  \includegraphics[width=\linewidth]{graphics/Image(5).jpg}
\endminipage\hfill
\minipage{.15\textwidth}%
  \includegraphics[width=\linewidth]{graphics/Image(6).jpg}
\endminipage
  \caption{(1) Andy is entering the floor and immediatly instructed to start running. The floor will begin to move under his feet. (2) When trees appear on the way, Andy has to jump over them. (3) When Andy unintentionally lands on a tree, he is punished with extra time (time is counting forwarsds and stopped, when one run is finished).}\label{fig:awesome_image3}
\end{figure}

\begin{figure}[!htb]
\minipage{.15\textwidth}
  \includegraphics[width=\linewidth]{graphics/Image(7).jpg}
\endminipage\hfill
\minipage{.15\textwidth}
  \includegraphics[width=\linewidth]{graphics/Image(8).jpg}
\endminipage\hfill
\minipage{.15\textwidth}%
  \includegraphics[width=\linewidth]{graphics/Image(9).jpg}
\endminipage
  \caption{(1) Andy runs over a beach and approaches water with ice floes on it. He is instructed to jump on them. (2) After jumping on the icefloes, he put his hand onto the other ice floes. (3) When an ice floe melts, others appear, Andy has to put the hand on.}\label{fig:awesome_image3}
\end{figure}

After a the ice floe game, the run proceeds as already shown in figure 3.

\begin{figure}[!htb]
\minipage{.15\textwidth}
  \includegraphics[width=\linewidth]{graphics/Image(10).jpg}
\endminipage\hfill
\minipage{.15\textwidth}
  \includegraphics[width=\linewidth]{graphics/Image(11).jpg}
\endminipage\hfill
\minipage{.15\textwidth}%
  \includegraphics[width=\linewidth]{graphics/Image(12).jpg}
\endminipage
  \caption{(1) Andy runs over a beach with wood planks and is instructed to build a bridge to cross the water. (2) Andy touches the floor with his hands on the woodplanks to collect one. (3) He touches the water to build a part of a bridge. (4) Andy did alternating (2) and (3), finished the bridge and proceeds his run.}\label{fig:awesome_image3}
\end{figure}
